```{r}
require(tidyverse)
require(data.table)
require(randomForest)
require(mclust)
require(rpart)
require(rpart.plot)
require(foreign)
require(e1071)
```
Selection
#Data Source
#https://www.kaggle.com/datasets/whenamancodes/credit-card-customers-prediction

Pre-processing
```{r}
require(stringr)
require(sqldf)

data <- read.csv('BankChurners.csv')

missing_data<-is.na(data)

missing_df<-as.data.frame(missing_data)

missing_df

```

Excellent: 0-10% utilization
Good: 10-30% utilization
Fair: 30-50% utilization
Poor: 50% or higher utilization
Transformation
```{r}
Transform <- data

Transform$Util_Rank<-sapply(Transform$)



```

Descriptive Analysis
Question1 - Basic Aggregration
```{r}
#Summarise the average credit limit by different card type

#count the number of different education level

#Summaries Average of Open to buy all Income Category

```

Question2 - Basic statics (Bar)
```{r}

```

Question3 - Basic statics (pie)
```{r}

```

Question4 - Relation(scatter)
```{r}

```

https://www.digitalocean.com/community/tutorials/normalize-data-in-r
https://stats.stackexchange.com/questions/298507/mclust-model-names-corresponding-to-common-models-i-e-those-used-for-lpa-lc
Modelname EEE = Equal variances and equal covariances
if you want to make the clustering like a matrix, try to use modelname EEE
Question5 - Clustering
```{r}

```

Question6 - pattern finding(CART tree)
```{r}

rpart.plot(Tree)
```

Question7 - classification(Naive Bias)
```{r}
#NB Classification


#new customers


#make an enquiry
predict()
```

Question8 - Prediction/simulation (random Forest)
```{r}
#model building


#model testing

#new customer


#choose one row data for testing
predict()
```

Evualtion
#Write you finding in Report, Thanks!
